---
title: "Scenario Analysis Report"
subtitle: "Spatial Planning Analysis"
date: "`r format(Sys.time(), '%d %B %Y, %H:%M')`"
format: 
  html:
    self-contained: true
    theme: cosmo
    toc: true
    toc-depth: 2
    code-fold: true
    df-print: paged
    embed-resources: true
params:
  solution_plot: NULL
  solution_plot_path: NULL
  target_plot: NULL
  target_plot_path: NULL
  cost_plot: NULL
  cost_plot_path: NULL
  climate_plot: NULL
  climate_plot_path: NULL
  details_table: NULL
  details_table_path: NULL
  solver_log: NULL
  cost_id: NULL
  climate_id: NULL
  timestamp: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8
)
```

**Report Generated:** `r params$timestamp`

**Cost Layer:** `r params$cost_id`

**Climate Layer:** `r if(params$climate_id == "NA" || is.null(params$climate_id)) "Not applied" else params$climate_id`

---

# Solution Map

This map shows the optimal planning scenario for the study area that meets the selected conservation targets while minimizing cost. Planning units selected for protection are shown in dark blue, while unselected units are shown in light blue.

```{r solution-map, fig.height=10}
if (!is.null(params$solution_plot)) {
  print(params$solution_plot)
} else if (!is.null(params$solution_plot_path) && file.exists(params$solution_plot_path)) {
  knitr::include_graphics(params$solution_plot_path)
} else {
  cat("No solution plot available.")
}
```

---

# Target Achievement

This plot shows the proportion of suitable habitat/area for each conservation feature that is included in the selected planning units. The dashed line represents the set target for each feature. Hollow bars with a black border indicate incidental protection of features not explicitly targeted in this analysis.

```{r targets-plot, fig.height=8}
if (!is.null(params$target_plot)) {
  print(params$target_plot)
} else if (!is.null(params$target_plot_path) && file.exists(params$target_plot_path)) {
  knitr::include_graphics(params$target_plot_path)
} else {
  cat("No target plot available.")
}
```

---

# Cost Analysis

This plot shows the spatial plan overlaid with the cost layer, illustrating how the chosen cost metric influences the selection of planning units.

```{r cost-plot, fig.height=10}
if (!is.null(params$cost_plot)) {
  print(params$cost_plot)
} else if (!is.null(params$cost_plot_path) && file.exists(params$cost_plot_path)) {
  knitr::include_graphics(params$cost_plot_path)
} else {
  cat("No cost plot available.")
}
```

---

# Climate Resilience {.conditional}

```{r climate-section, results='asis'}
if (!is.null(params$climate_plot) && params$climate_id != "NA" && !is.null(params$climate_id)) {
  cat("Kernel density estimates for the climate-resilience metric. Higher values represent areas likely to warm less and where biodiversity is more likely to be retained. The dark blue distribution shows the climate-resilience metric in selected planning units, while the light blue shows unselected areas.\n\n")
} else {
  cat("Climate-smart planning was not applied in this analysis.\n\n")
}
```

```{r climate-plot, fig.height=8}
if (!is.null(params$climate_plot) && params$climate_id != "NA" && !is.null(params$climate_id)) {
  print(params$climate_plot)
} else if (!is.null(params$climate_plot_path) && params$climate_id != "NA" && !is.null(params$climate_id) && file.exists(params$climate_plot_path)) {
  knitr::include_graphics(params$climate_plot_path)
}
```

---

# Feature Details

Summary table showing the target and achieved protection level for each conservation feature.

```{r details-table}
if (!is.null(params$details_table)) {
  knitr::kable(params$details_table, format = "html") |>
    kableExtra::kable_styling(
      bootstrap_options = c("striped", "hover", "condensed"),
      full_width = FALSE,
      position = "left"
    )
} else if (!is.null(params$details_table_path) && file.exists(params$details_table_path)) {
  dt <- utils::read.csv(params$details_table_path, check.names = FALSE)
  knitr::kable(dt, format = "html") |>
    kableExtra::kable_styling(
      bootstrap_options = c("striped", "hover", "condensed"),
      full_width = FALSE,
      position = "left"
    )
} else {
  cat("No details table available.")
}
```

---

# Solver Log

Complete log of the problem setup and solving process, including runtime, planning units selected, area covered, and cost metrics.

```{r solver-log}
if (!is.null(params$solver_log)) {
  cat("```\n")
  cat(params$solver_log)
  cat("\n```")
} else {
  cat("No solver log available.")
}
```

---

# Session Information

```{r session-info}
sessionInfo()
```
