---
title: "Comparison Analysis Report"
subtitle: "Side-by-side Scenario Comparison"
date: "`r format(Sys.time(), '%d %B %Y, %H:%M')`"
format:
  html:
    self-contained: true
    theme: cosmo
    toc: true
    toc-depth: 2
    code-fold: true
    df-print: paged
    embed-resources: true
params:
  comp_plot_path: NULL
  soln_plot_path: NULL
  target_plot_path: NULL
  cost_plot_path: NULL
  climate_plot_path: NULL
  details_table_path: NULL
  solver_log1: NULL
  solver_log2: NULL
  cost_id1: NULL
  cost_id2: NULL
  climate_id1: NULL
  climate_id2: NULL
  timestamp: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8
)
```

**Generated:** `r params$timestamp`
**Cost Layers:** `r paste(params$cost_id1, 'vs', params$cost_id2)`
**Climate Layers:** `r paste(if (is.null(params$climate_id1) || params$climate_id1=='NA') 'None' else params$climate_id1, 'vs', if (is.null(params$climate_id2) || params$climate_id2=='NA') 'None' else params$climate_id2)`

---

# Comparison Map

Overlay of Scenario 1 and Scenario 2 selections.

```{r comp-plot, fig.height=8}
if (!is.null(params$comp_plot_path) && file.exists(params$comp_plot_path)) {
  knitr::include_graphics(params$comp_plot_path)
} else {
  cat("No comparison plot available.")
}
```

---

# Scenario Maps

Side-by-side maps for the two scenarios.

```{r soln-plot, fig.height=10}
if (!is.null(params$soln_plot_path) && file.exists(params$soln_plot_path)) {
  knitr::include_graphics(params$soln_plot_path)
} else {
  cat("No scenario maps available.")
}
```

---

# Target Achievement

```{r target-plot, fig.height=8}
if (!is.null(params$target_plot_path) && file.exists(params$target_plot_path)) {
  knitr::include_graphics(params$target_plot_path)
} else {
  cat("No target plot available.")
}
```

---

# Cost Analysis

```{r cost-plot, fig.height=10}
if (!is.null(params$cost_plot_path) && file.exists(params$cost_plot_path)) {
  knitr::include_graphics(params$cost_plot_path)
} else {
  cat("No cost plot available.")
}
```

---

# Climate Resilience

```{r climate-section, results='asis'}
if (!is.null(params$climate_plot_path) && file.exists(params$climate_plot_path) && !(is.null(params$climate_id1) && is.null(params$climate_id2)) && !(params$climate_id1=='NA' && params$climate_id2=='NA')) {
  cat("Kernel density estimates for the climate-resilience metric for each scenario. Higher values represent areas likely to warm less and where biodiversity is more likely to be retained.\n\n")
} else {
  cat("Climate-smart planning was not applied in either scenario or no climate plot available.\n\n")
}
```

```{r climate-plot, fig.height=8}
if (!is.null(params$climate_plot_path) && file.exists(params$climate_plot_path)) {
  knitr::include_graphics(params$climate_plot_path)
}
```

---

# Feature Details

```{r details-table}
if (!is.null(params$details_table_path) && file.exists(params$details_table_path)) {
  dt <- utils::read.csv(params$details_table_path, check.names = FALSE)
  knitr::kable(dt, format = "html") |>
    kableExtra::kable_styling(
      bootstrap_options = c("striped", "hover", "condensed"),
      full_width = FALSE,
      position = "left"
    )
} else {
  cat("No details table available.")
}
```

---

# Solver Logs

## Scenario 1

```{r solver-log-1}
if (!is.null(params$solver_log1)) {
  cat("````\n")
  cat(params$solver_log1)
  cat("\n````")
} else {
  cat("No solver log available for Scenario 1.")
}
```

## Scenario 2

```{r solver-log-2}
if (!is.null(params$solver_log2)) {
  cat("````\n")
  cat(params$solver_log2)
  cat("\n````")
} else {
  cat("No solver log available for Scenario 2.")
}
```

---

# Session Information

```{r session-info}
sessionInfo()
```
